---
title: "MCBS"
author: "Anna Daccache"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r}
install.packages("survey")
install.packages("dplyr")
install.packages("tidyr")
install.packages("janitor")
```
<br />

Dataset is from the [Medicare Current Beneficiary Survey COVID-19 2020 Fall Supplement PUF](https://www.cms.gov/research-statistics-data-and-systems/downloadable-public-use-files/mcbs-public-use-file).

#### Dual Status and Telemedicine

```{r}
library("survey")
library(dplyr)


df = readr::read_csv("COVIDPUF_2_2020F.csv")


df = df %>%
  mutate(tele_med = case_when(ACV_TELMED == "1" ~ "_Yes",
                                ACV_TELMED == "2" ~ "_No",
                                ACV_TELMED == "D" ~ "_DK"),
         dual_var = case_when(DMV_H_OPMDCD == 1 ~ "Dual",
                                  DMV_H_OPMDCD == 2 ~ "Non_Dual",
                                  DMV_H_OPMDCD == 3 ~ "Partial",
                                  DMV_H_OPMDCD == 4 ~ "QMB_Only"),
         dual_var = factor(dual_var, levels = c("Dual", "Non_Dual", "Partial", "QMB_Only")))

```
<br />

##### Replicate Weights

```{r}

mcbs <- svrepdesign(
  weights = ~CPWFWGT,
  repweights = "CPWF[001-100]+",
  type = "Fay",
  rho = 0.3,
  data = df,
  combined.weights = TRUE
)

```

<br />

##### Comparing different dual status groups to examine provider's TM use.

```{r}
duals <- svyby(~tele_med, ~dual_var, mcbs, svymean, na.rm = TRUE, na.rm.all = TRUE)
print(duals)
```

```{r}
barplot(duals, main="Telemedicine Provision by Dual Status",
        xlab="Dual Status",
        ylab="Percent",
        col=c("darkblue", "lightblue", "blue"),
        legend = c("Don't Know", "No", "Yes"),
        args.legend = list(x = "bottomleft",
                           inset = c(-0.13, -0.32)))

```
<br />

#### Combining Duals Status groups vs NonDuals

Looking at Dual, Partial, and QMB against Non Duals.

```{r}
df1 = df %>%
  mutate(tele_med = case_when(ACV_TELMED == "1" ~ "_Yes",
                                ACV_TELMED == "2" ~ "_No"),
         dual_var = case_when(DMV_H_OPMDCD == 1 & 3 & 4 ~ "Combined_Dual",
                                  DMV_H_OPMDCD == 2 ~ "Non_Dual"),
         dual_var = factor(dual_var, levels = c("Combined_Dual", "Non_Dual")))
```

##### Replicate Weights

```{r}

mcbs <- svrepdesign(
  weights = ~CPWFWGT,
  repweights = "CPWF[001-100]+",
  type = "Fay",
  rho = 0.3,
  data = df1,
  combined.weights = TRUE
)

```

```{r}
duals_combo <- svyby(~tele_med, ~dual_var, mcbs, svymean, na.rm = TRUE, na.rm.all = TRUE)
print(duals_combo)
```
```{r}
barplot(duals_combo, main="Telemedicine Provision by Dual Status",
        xlab="Dual Status",
        ylab="Percent",
        col=c("darkblue", "lightblue"),
        legend = c("No", "Yes"),
        args.legend = list(x = "bottomleft",
                           inset = c(-0.13, -0.32)))

```

<br />

#### Gender and Telemedicine 

```{r}
df2 = df %>%
  mutate(tele_med = case_when(ACV_TELMED == "1" ~ "_Yes",
                                ACV_TELMED == "2" ~ "_No",
                                ACV_TELMED == "D" ~ "_DK"),
         gender = case_when(DMV_SEX == 1 ~ "Male",
                                  DMV_SEX == 2 ~ "Female"),
         gender = factor(gender, levels = c("Male", "Female")))
```

<br />

##### Replicate Weights

```{r}

mcbs <- svrepdesign(
  weights = ~CPWFWGT,
  repweights = "CPWF[001-100]+",
  type = "Fay",
  rho = 0.3,
  data = df2,
  combined.weights = TRUE
)

```

<br />

##### Examining TM status by gender.

```{r}
genderTM <- svyby(~tele_med, ~gender, mcbs, svymean, na.rm = TRUE, na.rm.all = TRUE)
print(genderTM)
```

```{r}
barplot(genderTM, main="Telemedicine Provision by Gender",
        xlab="Gender",
        ylab="Percent",
        col=c("darkblue", "lightblue", "blue"),
        legend = c("Don't Know", "No", "Yes"),
        args.legend = list(x = "bottomleft",
                           inset = c(-0.13, -0.32)))

```
<br />

#### Race and Telemedicine 

```{r}
df3 = df %>%
  mutate(tele_med = case_when(ACV_TELMED == "1" ~ "_Yes",
                                ACV_TELMED == "2" ~ "_No",
                                ACV_TELMED == "D" ~ "_DK"),
         race = case_when(DMV_RACE == 1 ~ "White (nh)",
                                  DMV_RACE == 2 ~ "Black (nh)",
                                  DMV_RACE == 3 ~ "Hispanic",
                                  DMV_RACE == 4 ~ "Other"),
         race = factor(race, levels = c("White (nh)", "Black (nh)", "Hispanic", "Other")))
```

<br />

##### Replicate Weights

```{r}

mcbs <- svrepdesign(
  weights = ~CPWFWGT,
  repweights = "CPWF[001-100]+",
  type = "Fay",
  rho = 0.3,
  data = df3,
  combined.weights = TRUE
)

```

<br />

##### Examining TM status by race.

```{r}
raceTM <- svyby(~tele_med, ~race, mcbs, svymean, na.rm = TRUE, na.rm.all = TRUE)
print(raceTM)
```

```{r}
barplot(raceTM, main="Telemedicine Provision by Race",
        xlab="Race",
        ylab="Percent",
        col=c("darkblue", "lightblue", "blue"),
        legend = c("Don't Know", "No", "Yes"),
        args.legend = list(x = "topright",
                           inset = c(-0.05, 0.32)))

```

<br />

#### Race and Dual Status 

```{r}
df4 = df %>%
  mutate(race = case_when(DMV_RACE == 1 ~ "White (nh)",
                                  DMV_RACE == 2 ~ "Black (nh)",
                                  DMV_RACE == 3 ~ "Hispanic",
                                  DMV_RACE == 4 ~ "Other"),
        dual_var = case_when(DMV_H_OPMDCD == 1 ~ "Dual",
                                  DMV_H_OPMDCD == 2 ~ "Non_Dual",
                                  DMV_H_OPMDCD == 3 ~ "Partial",
                                  DMV_H_OPMDCD == 4 ~ "QMB_Only"),
         dual_var = factor(dual_var, levels = c("Dual", "Non_Dual", "Partial", "QMB_Only")))
```

<br />

##### Replicate Weights

```{r}

mcbs <- svrepdesign(
  weights = ~CPWFWGT,
  repweights = "CPWF[001-100]+",
  type = "Fay",
  rho = 0.3,
  data = df4,
  combined.weights = TRUE
)

```

<br />

##### Examining Dual status by race.

```{r}
raceTM <- svyby(~race, ~dual_var, mcbs, svymean, na.rm = TRUE, na.rm.all = TRUE)
print(raceTM)
```

```{r}
barplot(raceTM, main="Dual Status by Race",
        xlab="Dual Status",
        ylab="Percent",
        col=c("darkblue", "lightblue", "blue", "white"),
        legend = c("Black", "White", "Hispanic", "Other"),
        args.legend = list(x = "topright",
                           inset = c(-0.05, 0)))

```








